---
title       : Developing Data Products Project
subtitle    : Inspecting the Phoenix Data Project
author      : LowTech
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Purpose

The Phoenix Data Project is an open source project for generating political event data--conflict (coups, wars, that kinda stuff) and cooperation (alliance activity, declarations of peace, etc.). Fun! I wanted to see what the data looked like, so I put this project together. It just looks at the # of recorded events per day, and the distribution of conflict and cooperation.

--- .class #id 

## Comparing Days: Event Counts

Example, 6/10/15

Download the specified day's file, read in the data. How many political events occurred? *

```{r, echo=FALSE}
# Add column names
colNames = c("EventID", "Date", "Year", "Month", "Day", "SourceActorFull", 
             "SourceActorEntity", "SourceActorRole", "SourceActorAttribute", 
             "TargetActorFull", "TargetActorEntity", "TargetActorRole", 
             "TargetActorAttribute", "EventCode", "EventRootCode", "PentaClass", 
             "GoldsteinScore", "Issues", "Lat", "Lon", "LocationName", "StateName", 
             "CountryCode", "SentenceID", "URLs", "NewsSources")
# Download file
fileName <- 'events.full.20150610.txt'
zipName <- paste(fileName, '.zip', sep = "")
webName <- paste('http://s3.amazonaws.com/openeventdata/current/', zipName, sep = "")
download.file(webName, zipName)
unzip(zipName)

# Read in data
data <- read.table(fileName, sep = "\t", col.names = colNames, comment.char = "", as.is = TRUE)

# Return the event count
nrow(data)
```

* The Phoenix Data Project processes a few hundred select known news sources, to try to get as much high quality coverage as possible. Of course, not all areas are covered equally (or at all).

--- .class #id 

## Comparing Days: Conflict/Cooperation

Example, 6/10/15

Goldstein Scores, from -10 to 10', -10 being most conflictual, 10 being most cooperative

```{r, echo=FALSE}
colNames = c("EventID", "Date", "Year", "Month", "Day", "SourceActorFull", 
             "SourceActorEntity", "SourceActorRole", "SourceActorAttribute", 
             "TargetActorFull", "TargetActorEntity", "TargetActorRole", 
             "TargetActorAttribute", "EventCode", "EventRootCode", "PentaClass", 
             "GoldsteinScore", "Issues", "Lat", "Lon", "LocationName", "StateName", 
             "CountryCode", "SentenceID", "URLs", "NewsSources")
data <- read.table(fileName, sep = "\t", col.names = colNames, comment.char = "", as.is = TRUE)
        
hist(data$GoldsteinScore)
```

--- .class #id 

## More info

For more information on the Phoenix Data Project, go to phoenixdata.org

You can follow (nearly) all of the collaborators on Twitter (they seem like nice people)
@charlie_simpson, @ahalterman, @johnb30, @PatrickTBrandt

And if you're really interested, I'm on the Internet, too: @petergowen

